Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-06-05 PAPER/main.tex
more bullet points to comparison/analysis section

\begin{itemize}
	\item optimality converge toward 1 as $\delta$ increases, i.e. as the problem instances become less difficult.
	\item When $\delta = 1.0$. MFFD and MFFD$^+$ perform identically, as the problems are equivalent to the original BPP, and so they behave like the original FFD heuristic.
	\item When $\delta = 0.0$, all optimalities are equal, as each item requires its own strip, and so $|\mathcal{I}|$ strips are needed for all 1000 instances.
	\item Values in bold represent the best avg optimality of the three heuristics for the given level of $\delta$. 
	\item Clear pattern across both set sizes, PS performs the best out of the three for $\delta = 0.1$ to 0.7 when $W = 5000$, and for $\delta = 0.1$ to 0.6 when $W = 2500$.
	\item However, when $W = 1250$, PS is only superior when $\delta = 0.1$ and 0.2. 
	\item On further inspection, we can see that the difference between the average optimalities for PS and MFFD$^+$ is negligible.
	\item Using Table 1 as an example, when $\delta = 0.2$, the solutions generated by PS are on average within 31.781\% of $t$, and for MFFD$^+$ within 32.61\%, a difference of 0.829\%. 
	\item In practical terms, PS produces solutions using 303.95 strips on average, where $t = 230.648$. MFFD$^+$ produces solutions using 305.862 strips, a difference of less than two strips. 
	\item Another trend is that PS produces average solutions within 10\% of $t$ for $\delta = 0.5$ onwards when $W = 5000$ and 2500, however when $W = 1250$, PS only produces solutions within 10\% of $t$ for $\delta = 0.8$ onwards.
	\item In contrast, MFFD and MFFD$^+$ can produce solution within 10\% of $t$ when $W = 1250$ for $\delta = 0.5$ onwards for $n = 500$, and $\delta = 0.4$ for $n = 1000$.
	\item MFFD$^+$ can also find solutions within 1\% of $t$ for $\delta = 0.8$ onwards for all strip widths in both set sizes.
	\item Number of items per strip smaller, problem is harder, falkenauer 1996, martello and toth 1990b
	\item 
\end{itemize}

>>>>

\begin{itemize}
	\item optimality converge toward 1 as $\delta$ increases, i.e. as the problem instances become less difficult.
	\item When $\delta = 1.0$. MFFD and MFFD$^+$ perform identically, as the problems are equivalent to the original BPP, and so they behave like the original FFD heuristic.
	\item When $\delta = 0.0$, all optimalities are equal, as each item requires its own strip, and so $|\mathcal{I}|$ strips are needed for all 1000 instances.
	\item Values in bold represent the best avg optimality of the three heuristics for the given level of $\delta$. 
	\item Clear pattern across both set sizes, PS performs the best out of the three for $\delta = 0.1$ to 0.7 when $W = 5000$, and for $\delta = 0.1$ to 0.6 when $W = 2500$.
	\item However, when $W = 1250$, PS is only superior when $\delta = 0.1$ and 0.2. 
	\item On further inspection, we can see that the difference between the average optimalities for PS and MFFD$^+$ is negligible.
	\item Using Table 1 as an example, when $\delta = 0.2$, the solutions generated by PS are on average within 31.781\% of $t$, and for MFFD$^+$ within 32.61\%, a difference of 0.829\%. 
	\item In practical terms, PS produces solutions using 303.95 strips on average, where $t = 230.648$. MFFD$^+$ produces solutions using 305.862 strips, a difference of less than two strips. 
	\item Another trend is that PS produces average solutions within 10\% of $t$ for $\delta = 0.5$ onwards when $W = 5000$ and 2500, however when $W = 1250$, PS only produces solutions within 10\% of $t$ for $\delta = 0.8$ onwards.
	\item In contrast, MFFD and MFFD$^+$ can produce solution within 10\% of $t$ when $W = 1250$ for $\delta = 0.5$ onwards for $n = 500$, and $\delta = 0.4$ for $n = 1000$.
	\item MFFD$^+$ can also find solutions within 1\% of $t$ for $\delta = 0.8$ onwards for all strip widths in both set sizes.
	\item Number of items per strip smaller, problem is harder, falkenauer 1996, martello and toth 1990b items per strip roughly 2
	\item all instances run in less than 160ms
	\item For each instance where opt $>1$, two cases: either $t$ is incorrect, and there does not exist a solution with $k = t$ strips, and the solution found is actually an optimal solution, or $t$ is correct, and the heuristic cannot find a solution with $t$ strips, not an optimal solution.
	\item since this is a relatively new problem, no problem instances solved to optimality, and so we have no way of knowing if in fact the heuristics are finding optimal solutions. Only able to compare with the theoretical minimum. 
\end{itemize}
